---
title: "Accessing the chunked graph server"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## tl;dr

To set up programmatic access to FlyWire, use `flywire_set_token()` as follows:

```{r, eval=FALSE}
library(fafbseg)
flywire_set_token()
```
and follow the on-screen prompts.

## Background

The main goal of connectomics is to trace (segment) the branching morphology of
neurons in any 3D volume (typically based on electron microscopy) and to 
identify the connections (synapses) between them that together define a 
connectome.

Neuron segmentation can be either skeleton-based 
(in which only the centre line defining each part of the neuronal arbour is traced out) 
or voxel-based, 
where a filled 3D structure is defined by labelling every voxel with an integer id, 
representing its membership of particular object; 
this is typically then displayed as a 3D mesh surface. Although skeleton-based
segmentation is more efficient for manual segmentation by humans, 
voxel-wise segmentation is more natural for machine learning algorithms.
Furthermore, it generates a richer representation of the neuron 
(capturing more of its structural features) and, crucially, 
also resolves ambiguities about object identity. 
For example when two users manually trace a neuron skeleton, 
they will place nodes in differentpositions and it is not trivial 
computationally to determine if they are part of the same object or how to join tracing of independent pieces together. 
In contrast in a voxel-wise segmentation every xyz location in the image is 
explicitly defined to be part of a specified object.

In a voxel-wise segmentation, each neuron can be considered as a collection of voxels grouped together as connected components. Machine learning based algorithms try to identify such connected components (e.g. using flood filling networks). However machines are not perfect and many segments are wrongly connected. Hence we need a step where humans proofread the segments and alters the connections. These connected components can be readily represented as vertices and the connections between them as edges. The human observer essentially modifies these edges in the graph structure. Note that this graph representation of object segmentation is distinct from the binary tree that represents the neuronal morphology or the connection graph of neurons within a
neural network.

This graph based representation of segmentation also has advantages for synchronous
editing, which can be a major technical issue if many users are to generate or
proof-read segmentation at the same time. 
The `CATMAID` web application (for skeleton based tracing) approaches this by
allowing multiple users to edit all neurons using a shared database. 
This implementation reduces conflicts by the simple expedient of allowing users 
to see each other's work in real time. 
However an explicit merge step is needed when conflicting annotations are created
(usually because editing has happened in different database) and this can be computationally complex. The [Seung Lab](https://seunglab.org/) has developed a data structure system called `chunked graph` that lets users modify segmentations (3D voxel-wise) in real-time and allows access to earlier versions of the segmentation. A brief overview of the system is published in [medium](https://medium.com/princeton-systems-course/building-a-multi-user-platform-for-real-time-very-large-graph-editing-ee37268025ad).

In practice an initial *over-segmentation* is generated, consisting of
many "supervoxels". These supervoxels, which are small collections of perhaps
tens to thousands of individual voxels, are effectively immutable but are almost 
certain to belong to the same object. It is these supervoxels which are the leaves
on the graph database representation of segmented objects. 
The use of supervoxels reduces the size of the graph database compared with the
situation in which individual voxel has to be represented.
So long as human proof-reading is based on the same base segmentation, there are
strategies to merge proof-reading even if this happens asynchronously.
However merging proof-reading based on different *base segmentations* defined by 
different underlying supervoxels is still complex; 
a similar challenge exists if it is necessary to map proof-reading based on one
base segmentation to a newer (presumably improved) base segmentation. 

## Goal

One of the goals in the **fafbseg** package is to provide access between different 3D segmentations of the `FAFB` dataset. Currently available segmentations include `FlyWire` (based on 3D CNNs : [U-Net](https://arxiv.org/abs/1709.02974)) and `GoogleBrain` (based on recursive CNNs : [flood-filling networks](https://www.nature.com/articles/s41592-018-0049-4)). Furthermore to enable location transfer and comparison with `CATMAID` (skeleton based) manual reconstruction. In order to achieve that one needs access to the 3D segmentations which are stored in a graph database  [Graphene/PyChunkedGraph](https://github.com/seung-lab/PyChunkedGraph). 
They also provide a Python tool called 
[CloudVolume](https://github.com/seung-lab/cloud-volume) which provides
programmatic access to the graph database.

## ChunkedGraph token

### Simple Instructions

You gain access to the `Graphene/Chunkedgraph` server by using a *token* which is
granted to you after you authenticate via a Google account. The simplest way to
do this is by doing

```{r, eval=FALSE}
library(fafbseg)
flywire_set_token()
```

This will offer to open your browser, generate a new token and save it in
a standard location. **Note that this will invalidate your previous token**!

### Details

The manual steps that `flywire_set_token()` tries to automate are are as follows

1. Visit https://globalv1.flywire-daf.com/auth/api/v1/refresh_token,
2. Copy the token present there, let's say it was "xxyyzz"
3. create a file named `chunkedgraph-secret.json` at location `~/.cloudvolume/secrets/chunkedgraph-secret.json`. For example, in Terminal: 
```bash
mkdir -p .cloudvolume/secrets/
touch ~/.cloudvolume/secrets/chunkedgraph-secret.json
open ~/.cloudvolume/secrets/chunkedgraph-secret.json -e
```
4. Paste in the following contents
```json
{
  "token": "xxyyzz"
}
```

5. Save the file
6. Now you have access to the chunked graph server
