---
title: "Capturing neuroglancer meshes from a browser scene"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Background

Originally **fafbseg** had no support for reading objects directly from a
neuroglancer scene URL. The only approach was to capture an interactive web session.
Things have moved on with the ability to read meshes directly from the brainmaps
API via `read_brainmaps_meshes()` or 
using the [CloudVolume](https://github.com/seung-lab/cloud-volume) interface
via `read_cloudvolume_meshes()`. However this information is being retained for
reference and might be helpful when direct mesh retrieval is not yet available.

## Method

You should make sure that you only have one neuron displayed if you
do not want to have to parse the object identifier relationships.

With Chrome you can generate an appropriate set of curl download commands by:

1. Opening the Chrome Developer console (View ... Developer ... JavaScript Console),
2. (re)loading a page of interest
3. selecting the network tab
4. selecting a downloaded object 
5. right clicking and then choosing (Copy ... **Copy all as cURL**).

You can either save the contents of the clipboard into a text file (e.g. 
`all_curl.sh`) or just keep it in the clipboard.

You can then go to R and proceed as follows

```{r setup, eval=FALSE}
library(fafbseg)
# omit the first argument if you want to use the clipboard
fetch_all_curl("all_curl.sh", outdir="alldata",
  regex="brainmaps.googleapis.com", fixed=TRUE)
meshdata=read_ng_dump("alldata")
library(elmr)
# or whatever your CATMAID neuron skid is
y=read.neuron.catmaid(23432)
compare_ng_neuron(meshdata, y)
```
